\documentclass[../article.tex]{subfiles}

\begin{document}

\section{The Discrete Fourier Transform}
Our purpose in this section is to give the reader an understanding of the theoretical framework which gives rise to the Discrete Fourier transform.

\subsection{The Signal Interpretation of the Discrete Fourier Transform}

Let $f(t)$ be a periodic function. Then the discrete Fourier transform of $f(t)$, called $\mathcal{F}\{f(t)\}$, is the value of the amount of frequency given by $f(t)$. Consider a set of samples $S = \{0,1,2,...,T-1\}$. Then the discrete Fourier transform of $f(S)$ is
<<<<<<< HEAD

\[
F(n) = \sum_{k=0}^{T-1} f(k) e^{-2 \pi ikn/T}
\]

where $n \in \mathbb{Z}$.
=======
\begin{equation*}
F(n) = \sum_{k=0}^{T-1} f(k) e^{-2 \pi ikn/T}
\end{equation*}

where $n \in \mathbb{Z}$.

>>>>>>> 58dfdedc76a6c44255dc0279a9f7ba7462651506

\subsection{The Group $\mathbb{Z}(N)$}

As it turns out, the group $\mathbb{Z}(N)$ plays an important part in the theory of the discrete Fourier transform, and acts as a weight for storing information on the unit circle for any given periodic function.

\begin{definition}
Let $\mathbb{Z}(N)$ be the set of all N-th roots of unity. Then,
 \[Z(N) = \{z \in C : z^N = 1 \}\]
\end{definition}
\begin{theorem}
For all $N \in \mathbb{Z}$, we have that
\[\mathbb{Z}(N)= \left\{1, e^{(2 \pi i)/N}, e^{(4 \pi i)/N}, \ldots, e^{(2(N-1) \pi i)/N}\right\}\]
\end{theorem}

\begin{proof}
Let $z$ $\in \mathbb{Z}(N)$. Then, $z^N = (r \cdot e^{i \theta})^N = 1$. Therefore, $\mid r^N \mid \mid e^{i N \theta} \mid = 1$. Hence, $r = e^{i N \theta} = 1$. Therefore, $N\theta = 2k\pi$, where $k \in \mathbb{Z}$. Let $\zeta$ = $e^{2 \pi i /(N-1)}$. Then,
\begin{align*}
	(\zeta^0)^N &= e^0 = 1 \\
	(\zeta^1)^N &= e^{2 \pi i} = 1 \\
	(\zeta^2)^N &= e^{4 \pi i} = 1 \\
	{} &\vdotswithin{=}\\
	(\zeta^{N-1})^N &= (e^{2 \pi i(N-1)/N})^N \\
	{} &= (e^{2 \pi i}e^{-2 \pi i/N})^N \\
	{} &= 1 \cdot e^{-2 \pi i} \\
	{} &= 1
\end{align*}
Therefore, $\zeta^k \in \mathbb{Z}(N)$ for all $k$ such that $0 \leq k \leq N-1$. Notice that the set $Q = \{0, 1, 2, \ldots, N-1\}$ is a residue system modulo $N$, and that the set $\zeta^Q = \left\{1, e^{2 \pi i/N}, e^{4 \pi i/N}, \ldots, e^{2(N-1) \pi i/N}\right\} \subseteq \mathbb{Z}(N) $.
Now, for every $n \in \mathbb{Z}$, there exists an integer $m \in Q$ such that $n \equiv m \mod N$, since $Q$ is a complete residue system modulo $N$. When $k \geq N-1$, we have that $k \equiv l \mod N$ for some $l \in Q$. Therefore, $\mathbb{Z}(N) \subseteq Q$, and since we know $Q \subseteq Z(N)$, we have $Q = Z(N)$.
\end{proof}

We can also show that $\mathbb{Z}(N)$ is a finite abelian group and, indeed, forms a basis of a vector space of complex-valued functions on the unit circle.

\begin{theorem}
$\mathbb{Z}(N)$ is a finite abelian group.
\end{theorem}

\begin{proof}
That $| \mathbb{Z}(N)| < \infty$ is self-edvident. Thus, $\mathbb{Z}(N)$ is a finite group. Letting $z,w \in \mathbb{Z}(N)$, we find that $z \cdot w = e^{2 \pi i (k+l)/N}$ for some $k,l \in \mathbb{Z}$. Then, by the complete residue theorem of number theory, there exists an $m \in \{1, 2, 3, ..., N-1\}$ such that $(k+l) \equiv m \mod N$. Hence, $e^{2 \pi i (k+l)/N} = e^{2 \pi i m/N} \in \mathbb{Z}(N)$. Therefore, $\mathbb{Z}(N)$ is closed under complex multiplication. Let $z,w \in \mathbb{Z}(N)$. Then $z \cdot w = e^{2 \pi i k/N} \cdot e^{2 \pi i l/N} = e^{2 \pi i (k+l)/N} = e^{2 \pi i (l+k)/N} = e^{2 \pi i l/N} \cdot e^{2 \pi i k/N} = w \cdot z$. Therefore $(\mathbb{Z}(N), \cdot)$ is commutative. Next, let $z,w,s \in \mathbb{Z}(N)$. Then, $(z \cdot w) \cdot s = (e^{2 \pi i k/N} \cdot e^{2 \pi i l/N}) \cdot e^{2 \pi i t/N} = e^{2 \pi i ((k+l)+t)/N} = e^{2 \pi i (k+(l+t))/N} = e^{2 \pi i k/N} \cdot (e^{2 \pi i l/N} \cdot e^{2 \pi i t/N}) = z \cdot (w \cdot s)$. So $(\mathbb{Z}(N), \cdot)$ is associative. The identity element is $1 \in \mathbb{Z}(N)$, since for all $z \in \mathbb{Z}(N)$ we have $z \cdot 1 = z$. If $z \in \mathbb{Z}(N)$, then $(1/z)^N = 1/ z^N = 1$. Therefore, $1/z \in \mathbb{Z}(N)$ and the inverse of any $z \in \mathbb{Z}(N)$ is $1/z$. Therefore, $\mathbb{Z}(N)$ is an abelian group.
\end{proof}

Furthermore, we can show that $\mathbb{Z}/ N\mathbb{Z}$, the set of all equivalence classes of integers modulo $N$, is an abelian group.

\begin{definition}
For all $x \in \mathbb{Z}$, let $R_N (x) = \{y \in \mathbb{Z} : y \equiv x   \mod   N\}$, where $N \in \mathbb{Z}$
\end{definition}
\begin{theorem}
For all $x,y \in \mathbb{Z}$, $R_N (x) + R_N (y) = R_N (x+y).$
\end{theorem}
\begin{proof}
Let $\alpha \in R_N (x)$ and $\beta \in R_N (y)$. Then, $\alpha = x +kN$ for some $k \in \mathbb{Z}$ and $\beta = y + lN$ for some $l \in \mathbb{Z}$. Then, $(x+y)+(k+l)N \in R_N (x+y)$. Conversely, let $x+y \in R_N (x+y)$. Then, $x = \alpha -kN$ and $y = \beta -lN$. Therefore, $(x+y) = (\alpha + \beta) -(k+l)N$. Therefore, $(x+y) \equiv \alpha +\beta) \mod N$. Therefore, $x \equiv \alpha \mod N$ and $y \equiv \beta \mod N$. Therefore, $x+y \in R_N (x) + R_N (y)$.
\end{proof}

Now that we have proven $\mathbb{Z}(N)$ is a finite abelian group and homomorphic to the group $\mathbb{Z} /N\mathbb{Z}(N)$, we can think of the discrete Fourier transform as a vector space over $\mathbb{Z}(N)$ with the Hermitian inner product


\[
  (F,G) = \sum_{n=0}^{N-1} F(k) \overline{G(k)}
\]
and norm

\[
  ||F||^2 = \sum_{k=0}^{N-1} |F(k)|^2
\]


\begin{theorem}
If $F$ is a function on $\mathbb{Z}(N)$, then
\[
F(k) = \sum_{n=0}^{N-1} a_n e^{2 \pi nk/N}
\]
where
\[
a_n = \frac{1}{N} \sum_{k=0}{N-1} F(k) e^{-2 \pi ikn/N}.
\]
\end{theorem}
\begin{proof}
Let $\zeta^{lk} = e^{2 \pi i lk/N}$, where $k,l = 0,1,...N-1$. Then, the set
\[
V = \left\{ \frac{1}{\sqrt{N}}, \frac{1}{\sqrt{N}}e^{2 \pi i k/N}, \ldots, \frac{1}{\sqrt{N}}e^{2 \pi i k(N-1)/N} \right\}
\]
forms an orthogonal basis for $\mathbb{Z}(N)$. So,
\[
F(k) = \sum_{n=0}^{N-1} \Big(F(k), \frac{1}{\sqrt{N}}\zeta^{nk} \Big) \frac{1}{\sqrt{N}}\zeta^{nk}
\]
where $\big(F,G \big)$ represents the Hermitian product of $F$ and $G$. By substitution we obtain
\begin{align*}
F(k) &= \sum_{n=0}^{N-1} \Bigg(\sum_{k=0}^{N-1} F(k) \frac{1}{\sqrt{N}} \zeta^{-lk} \Bigg) \frac{1}{\sqrt{N}} \zeta^{lk} \\
&= \sum_{n=0}^{N-1} \Bigg(\frac{1}{N} \sum_{k=0}^{N-1} F(k) \zeta^{-lk} \Bigg) \zeta^{lk} \\
&= \sum_{n=0}^{N-1} a_n e^{2 \pi nk/N}
\end{align*}
where
\[
a_n = \frac{1}{N} \sum_{k=0}^{N-1} F(k) e^{-2 \pi ikn/N}
\]
and $e^{2 \pi i/N} = \zeta$.
\end{proof}

With the discrete Fourier transform defined, it is now possible to define the Fast Fourier Transform, which is the subject of the next section.

\end{document}
